---
title: "GENIECnaClinical"
author: "Kaleb Olson"
date: "March 10, 2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggplot2)
library(dplyr)
library(reshape2)
library(magrittr)
library(ggbiplot)
library(readr)
library(synapseClient)
synapseLogin()
```

## CNA and Clinical Data Exploration

First we get the data file from synapse and read it in. Because synapse checks if the file is in the cache before downloading.
```{r}
syn.clin <- synGet('syn7851246')
syn.cna <- synGet('syn7851245')
cna <- read_tsv(syn.cna@filePath)
clin <- read_tsv(syn.clin@filePath)
```
Here is a summary of the counts of the different types of cancer from GENIE

```{r}
summary(factor(clin$CANCER_TYPE))
```
And how many individuals vs samples? We see that the max is 4 samples per individual.
```{r}
clin.smplPerIndv <- as.data.frame(summary(factor(clin$PATIENT_ID)), row.names = NULL)
```

We need to reshape (melt and cast) the cna data before we can match up the SAMPLE_ID variable between cna and clin.
```{r}
cna.mltd <- melt(cna)
cna.cst <- dcast(cna.mltd, variable ~ ...)
colnames(cna.cst)[1] <- "SAMPLE_ID"
```

Let's try joining the clinical and cna data. We also get a vector of the order of HUGO names.
```{r}
cnaclin <- inner_join(clin, cna.cst)
hugosym.sorted <- sort(cna[[1]])
```
Let's make a vector mask to filter the data rows that have only records with +2 or -2 in at least one column.
```{r}
registerDoParallel() # so we can use do par below
cnaclin.posmask <- foreach(i=hugosym.sorted) %dopar% (cnaclin[[i]] == 2) %>% 
  Reduce(`|`, .)
cnaclin.negmask <- foreach(i=hugosym.sorted) %dopar% (cnaclin[[i]] == -2) %>%
  Reduce(`|`, .)
```

And now masking the data...
```{r}
cnaclin.pos <- cnaclin[cnaclin.posmask,]
cnaclin.neg <- cnaclin[cnaclin.negmask,]
```

Question: are these data too reduced? Here is the number of records excluded from the main for not having extreme values. Note that there can be overlap e.g., a single record might be substracted twice from nrow if it has both -2 and +2. Thus this count is lower bound.
```{r}
nrow(cnaclin) - (nrow(cnaclin.neg) - nrow(cnaclin.pos))
```




