---
title: "PipelineDevelopment"
author: "Kaleb Olson"
date: "April 13, 2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggplot2)
library(dplyr)
library(reshape2)
library(magrittr)
library(readr)
library(synapseClient)
library(doParallel)
library(tidyverse)
```


```{r}
synapseLogin()
```

Load all the data we want to work with.
```{r}
genie.filtered.cn <- readRDS("genie-filtered-cn.rds")
gdsc.filtered.cn <- readRDS("gdsc-filtered-cn.rds")
gdsc.filtered.cn.t <- readRDS("gdsc-filtered-cn-t.rds")

celline.to.cosmicid <- readRDS("gdsc-cellline-to-cosmic-id.rds")
screeened.compounds <- readRDS("screened-compounds.rds")
dose.response <- readRDS("dose-response.rds")

genie.clin <- readRDS("genie-clin.rds")
intersecting.genes <- readRDS("intersecting-genes.rds")
genie.filtered.cnclin <- readRDS("genie-filtered-cn-clin.rds")


genie.subsets.cn.profiles.old <- readRDS("genie.subsets.cn.profiles.rds")
gdsc.subsets.cn.profiles <- readRDS("Drug-Profile-Table.rds")
genie.subsets2060.cn.profiles <- readRDS("latest.genie.subset.cn.profiles.rds")
```

Make a tree map breakdown of cancer and cancer sub-type.
```{r}
#test.count <- genie.clin %>% group_by(CANCER_TYPE_DETAILED) %>% mutate(COUNT = n())
#png(filename="tree.png",width=1024, height=600);
#treemap(test.count, index=c("CANCER_TYPE", "CANCER_TYPE_DETAILED"), vSize = "COUNT", type="index", palette= "Reds", align.labels = list(c("center", "center"), c("right", "bottom")), title="GENIE - Breakdown by cancer and cancer sub-type", fontsize.labels=c(18,10), fontsize.title = 18);
#dev.off()
```

Example of how genie.filtered.cnclin is generated:
```
syn.clin <- synGet('syn7851246')
genie.clin <- read_tsv(syn.clin@filePath)
genie.filtered.cn.cst <- melt(genie.filtered.cn) %>% dcast(variable ~ ...)
colnames(genie.filtered.cn.cst)[1] <- "SAMPLE_ID"
genie.filtered.cnclin <- inner_join(genie.clin, genie.filtered.cn.cst)
saveRDS(genie.filtered.cnclin, "genie-filtered-cn-clin.rds")
```

Here is how the transposed and trimmed version of gdsc.filtered.cn was generated
```{r}
gdsc.filtered.cn.t <- as.data.frame(t(gdsc.filtered.cn))[c(-2, -3, -4),]

```

```{r}
translate <- function(quaddle) {
  maxchar <- substr(quaddle, 1, 1)
  max <- as.numeric(maxchar)
  if (!is.na(max) && max >= 9) {
    2
  }
  else if (!is.na(max) && max < 9) {
    switch(maxchar,
           "0" = -2,
           "1" = -1,
           "2" = 0,
           "3" = 1,
           "4" = 2,
           "5" = 2,
           "6" = 2,
           "7" = 2,
           "8" = 2)
  }
  else{
    NA
  }
}

gdsc.filtered.cn.trans <- apply(gdsc.filtered.cn.t, c(1,2), translate)
```

Here we check the gene EFGR (row number 138 in each dataset because we ordered genes alphabetically) to check that we get a comparable distribution of cnv values. This depends on an accurate translation of cnv data from gdsc style to genie style. The EFGR gene can be considered as a baseline because ...
```{r}
gdsc.efgr <- table(sapply( gdsc.filtered.cn[138, 5:ncol(gdsc.filtered.cn)],  translate))
genie.efgr <- table(unlist(genie.filtered.cn[138, 2:ncol(genie.filtered.cn) ]))
sapply(gdsc.efgr, function(x) x/ncol(gdsc.filtered.cn))
sapply(genie.efgr, function(x) x/ncol(genie.filtered.cn))

```
ERBB2
```{r}
gdsc.efgr <- table(sapply( gdsc.filtered.cn[150, 5:ncol(gdsc.filtered.cn)],  translate))
genie.efgr <- table(unlist(genie.filtered.cn[150, 2:ncol(genie.filtered.cn) ]))
sapply(gdsc.efgr, function(x) x/ncol(gdsc.filtered.cn))
sapply(genie.efgr, function(x) x/ncol(genie.filtered.cn))

```

Question: how many times does max not equal min in the unconverted GDSC data?
```{r}
maxeqmin <- function(x) {
  max_r <- substr(x, 1,1)
  min_r <- substr(x, 3,3)
  max_r == min_r
}


tout <- apply(gdsc.filtered.cn.t[2:nrow(gdsc.filtered.cn.t),], c(1,2), maxeqmin)
table(tout)

```
Question: how many times do we find that if the two don't match that the max is greater than 8
```{r}
maxneandgt8 <- function(x) {
  quad <- unlist(strsplit(x, ","))
  max_r <- quad[1]
  min_r <- quad[2]
  max_i = as.numeric(max_r)
  
  if (max_i != min_r){
     max_i >= 4
  }
  else {
    FALSE
  }
}
mout <- apply(gdsc.filtered.cn.t[2:nrow(gdsc.filtered.cn.t), ], c(1,2), maxneandgt8)
table(mout)
```

```{r}
bettertrans <- function(x){ 
  quad <- unlist(strsplit(x, ","))
  max_i <- as.numeric(quad[1])
  min_i <- as.numeric(quad[2])
  
  if (max_i == 0){
    -2
  }
  else if (max_i == 1) {
    -1
  }
  else if (max_i <= 3) {
    0
  }
  else if (max_i <= 8 && min_i < 8 ) {
    1
  }
  else {
    2
  }
}

gdsc.filtered.cn.bettertrans <- apply(gdsc.filtered.cn.t[2:nrow(gdsc.filtered.cn.t), ], c(1,2), bettertrans)
gdsc.cn.table <- as.data.frame(table(gdsc.filtered.cn.bettertrans))
colnames(gdsc.cn.table) <- c("cn", "freq")
```

```{r}
wipenonextr <- function(x){
  if (x != -2 || x != 2) {
    0
  }
  else {
    x
  }
}

sum(genie.filtered.cn[,2:ncol(genie.filtered.cn)] == -2) +
sum(genie.filtered.cn[,2:ncol(genie.filtered.cn)] == 2)
```

Make a plot of the distribution:
```{r}
genie.cn.table <- as.data.frame(table(unlist(genie.filtered.cn[,2:ncol(genie.filtered.cn)])))
colnames(genie.cn.table) <- c("cn", "freq")
```

```{r}
library(scales)
ggplot(genie.cn.table[-2,]) + geom_col(aes(x = cn, y = freq), fill="#B22222") + scale_y_log10( breaks = trans_breaks("log10", function(x) 10^x), labels = trans_format("log10", math_format(10^.x))) + labs(x="Discrete CN Level", y ="Count", title="GENIE Copy Number Distribution")

ggplot(gdsc.cn.table) + geom_col(aes(x = cn, y = freq), fill="#B22222") + scale_y_log10( breaks = trans_breaks("log10", function(x) 10^x), labels = trans_format("log10", math_format(10^.x))) + labs(x="Discrete CN Level", y ="Count", title="Translated GDSC Copy Number Distribution")
```


Now we choose a drug that is has at least one record that is very low IC50. In this case #104. We filter for this drug and any record that is less than our threshold of -2 for IC50
```{r}
gdsc.filtered.cn.bettertrans.df <- as.data.frame(gdsc.filtered.cn.bettertrans)
colnames(gdsc.filtered.cn.bettertrans.df) <- unlist(intersecting.genes)

library(data.table)
gdsc.filtered.cn.bettertrans.df <- setDT(gdsc.filtered.cn.bettertrans.df, keep.rownames = TRUE)[]
colnames(gdsc.filtered.cn.bettertrans.df)[1] <- "COSMIC_ID"

```

Now we show a trivial example of how we are going to compare profile sets. Note- that we will need to consider the positive 2 and the negative 2 cases individually.
```{r}
drug_id = 104
drug.experiments <- filter(dose.response, DRUG_ID == drug_id, LN_IC50 < -2)
profilein.2 <- filter(gdsc.filtered.cn.bettertrans.df, COSMIC_ID %in% drug.experiments$COSMIC_ID)

drug_id = 201
drug.experiments <- filter(dose.response, DRUG_ID == drug_id, LN_IC50 < -2)
profilein.1 <- filter(gdsc.filtered.cn.bettertrans.df, COSMIC_ID %in% drug.experiments$COSMIC_ID)

profile.104 <- apply(unlist(profilein.2 == 2), 2, function(x) sum(x)/length(x))
profile.201 <-  apply(unlist(profilein.1 == 2), 2, function(x) sum(x)/length(x))
dist(rbind(profile.201, profile.104), method = "euclidian")
```

We generalize the above as functions:
```{r}
colProp <- function(col) {sum(col)/length(col)}

mkProfile <- function(set, cnlevel) {
  props <- apply(unlist(set == cnlevel), 2, colProp)
  props <- props - mean(props)
  props
}

profileDist <- function(p1, p2) {dist(rbind(p1, p2), method = "euclidian")}

subsetDist <- function(set_a, set_b, cnlevel) {
  profileDist(mkProfile(set_a, cnlevel), mkProfile(set_b, cnlevel))
}

compareDrugs <- function(drug_id1, drug_id2, threshold, cnlevel) {
  mkRecordSet <- function(drug_id, threshold) {
    drug.experiments <- filter(dose.response, DRUG_ID == drug_id, LN_IC50 < threshold)
    records <- filter(gdsc.filtered.cn.bettertrans.df, COSMIC_ID %in% drug.experiments$COSMIC_ID)
    #assertthat::assert_that(length(records) >= 100)
    records
  }
  
  subsetDist(mkRecordSet(drug_id1, threshold), mkRecordSet(drug_id2, threshold), cnlevel)
}

```

This is where we rank the Strongest Drugs by LN and AUC
```{r}
#Drugs with most cell line responders.
strongestDrugs <- dose.response %>% filter(LN_IC50 < -2, AUC > .5) %>% group_by(DRUG_ID) %>% summarise(drugPower = sum(LN_IC50 < -2)) %>% arrange(desc(drugPower))

testableDrugs <- filter(strongestDrugs, drugPower > 10, drugPower < 100)

creamTestDrugs <- filter(dose.response, dose.response$DRUG_ID %in% testableDrugs$DRUG_ID, LN_IC50 < -2, AUC > .5) %>% arrange(DRUG_ID, LN_IC50)
testd <- data.table(creamTestDrugs)
setkey(testd, DRUG_ID)
creamTestDrugs <- testd[, lapply(.SD, function(x) head(x,10)), by = key(testd)]

# How many entries are eliminated by filtering AUC
LN_Filtered_Count <- dose.response %>% filter(LN_IC50 < -2) %>% nrow()
LN_AUC_filtered_Count <- dose.response %>% filter(LN_IC50 < -2, AUC > .5) %>% nrow()
AUC_Count <- LN_Filtered_Count - LN_AUC_filtered_Count
AUC_Count
#filter(strongestDrugs, stronge)
```


```{r}
# Create GDSC Drug Id CNLevel Profile Table, Parameters = cnLevels v(), drugIds v(), IC_50 threshold
makeDrugCNProfileTable <- function(cnlevels, drugIDs, threshold){
  headerLine <- c("DRUG_ID", "CN_LEVEL", unlist(intersecting.genes))
  gdsc.drug.cn.profile <- data.frame(matrix(ncol = length(headerLine), nrow = 0))
  for(drugID in drugIDs)
  {
    for(copyLevel in cnlevels)
    {
    drug.experiments <- filter(creamTestDrugs, DRUG_ID == drugID, LN_IC50 < threshold)
    records <- filter(gdsc.filtered.cn.bettertrans.df, COSMIC_ID %in% drug.experiments$COSMIC_ID)
    profile <- mkProfile(records, copyLevel)
    gdsc.drug.cn.profile <- rbind(gdsc.drug.cn.profile, c(drugID, copyLevel, unlist(profile)[-1]))
    }
  }
  colnames(gdsc.drug.cn.profile) <- headerLine
  return (gdsc.drug.cn.profile)
}

```

Generate GDSC drug profile table
```{r}
gdsc.subsets.cn.profiles <- makeDrugCNProfileTable(c(-2, -1, 1, 2), testableDrugs$DRUG_ID, -2)
```





```{r}

  mkRecordSet <- function(drug_id, threshold) {
    drug.experiments <- filter(dose.response, DRUG_ID == drug_id, LN_IC50 < threshold)
    records <- filter(gdsc.filtered.cn.bettertrans.df, COSMIC_ID %in% drug.experiments$COSMIC_ID)
    assertthat::assert_that(length(records) >= 100)
    records
  }

```

Where we checked to see if CDKN2B occurred most frequently as max gene.
```{r}
ids <- arrange(dose.response, LN_IC50)$DRUG_ID
trt<- function(id) {which.max((mkProfile(mkRecordSet(id, 2), -2)))}
sapply(unlist(ids[1:50]), trt)
```
Let's try plotting above.
```{r}
#install.packages("ggrepel") 
library("ggrepel")
profbyid <- function(id) {
  res <- as.data.frame(mkProfile(mkRecordSet(id, 2), -2))
  colnames(res) <- "SCORE"
  res <- tibble::rownames_to_column(res, "GENE")
  res
}

plotDrug <- function(id) {
  profile <- profbyid(id)
  name <- select(filter(screeened.compounds, `Drug ID` == id), `Drug Name`) 
  ggplot(profile, aes(x=GENE, y=SCORE)) + scale_y_log10() + geom_point() + geom_text_repel(data= subset(profile, SCORE > 0.001), aes(label=GENE), size = 3) + theme(axis.text.x=element_blank(), axis.ticks.x=element_blank()) + annotation_logticks(side="l") + labs(title = paste(name ," (", id, ") ", "CNV profile", sep=""))
}
```

```{r}

plotFilteredSubset <- function(id) {
  # NOT WORKING YET
  profile <- as.data.frame(filter(genie.subsets.cn.profiles, FILTER_ID == id)[,c(-1, -2)])
  colnames(profile) <- "SCORE"
  res <- tibble::rownames_to_column(res, "GENE")
  
  name <- "TODO"
  ggplot(profile, aes(x=GENE, y=SCORE)) + scale_y_log10() + geom_point() + geom_text_repel(data= subset(profile, SCORE > 0.001), aes(label=GENE), size = 3) + theme(axis.text.x=element_blank(), axis.ticks.x=element_blank()) + annotation_logticks(side="l") + labs(title = paste(name ," (", id, ") ", "CNV profile", sep=""))
}


```

Here is the function that will get the distance from each GENIE tumour subset to each GDSC drug subset.
```{r}
getTumourDrugDist <- function(subsetid, subsetTable, drugid, drugTable, cnlevels){
  totalDist = 0
  for (level in cnlevels) {
    subsetprofile <- unlist(filter(subsetTable, FILTER_ID == subsetid, CN_LEVEL == level)[,c(-1, -2)])
    drugprofile <- unlist(filter(drugTable, DRUG_ID == drugid, CN_LEVEL == level)[,c(-1, -2)])
    totalDist <- totalDist + profileDist(subsetprofile, drugprofile)
  }
  totalDist
}



rankDrugsBySubset <- function(subsetid, cnlevels) {
  sapply(unique(gdsc.subsets.cn.profiles$DRUG_ID), getTumourDrugDist, subsetid = subsetid, subsetTable = genie.subsets.cn.profiles, drugTable = gdsc.subsets.cn.profiles, cnlevels = cnlevels)
}

generateTumourDrugMatrix <- function(subsetprofile.df, drugprofile.df, cnlevels) {
  resultsTable <- as.data.frame(matrix(ncol = length(unique(drugprofile.df$DRUG_ID)), nrow = 0))
  for (subsetprofile in unique(subsetprofile.df$FILTER_ID)){
        cancerSubset_Row <- vector(mode = 'double')
    for (drugprofile in unique(drugprofile.df$DRUG_ID)){
      distance <- getTumourDrugDist(subsetprofile, subsetprofile.df, drugprofile, drugprofile.df, cnlevels)
      cancerSubset_Row <- append(cancerSubset_Row, distance)
    }
    resultsTable <- rbind(resultsTable, cancerSubset_Row)
  }
  colnames(resultsTable) <- unlist(unique(drugprofile.df$DRUG_ID))
  rownames(resultsTable) <- unlist(unique(subsetprofile.df$FILTER_ID))
  return (resultsTable)
}

```

```{r}

ResultsMatrix <- generateTumourDrugMatrix(genie.subsets2060.cn.profiles, gdsc.subsets.cn.profiles, c(-2,2))

```

Plot our heat map
```{r}
ResultsMatrix <- setDT(as.data.frame(testResult), keep.rownames = TRUE)[]
colnames(ResultsMatrix)[1]<- "FILTER_ID"

ResultsMatrix.m <- melt(ResultsMatrix)
colnames(ResultsMatrix.m) <- c("FILTER_ID", "DRUG_ID", "SCORE")
ggplot(ResultsMatrix.m, aes(DRUG_ID, FILTER_ID)) + geom_tile(aes(fill=SCORE)) + scale_fill_gradientn(colours = rainbow(7)) + theme(axis.text.x=element_text(angle = 45, hjust = .9, vjust = 1)) + labs(title="Drug CNV Score Matrix", x="Drug ID", y="Subset ID", key="Score")

```



------------------Subtyping GENIE ----------------------
```{r}
#transpose the genie filtered CN df
genie.filtered.cn.t <- t(genie.filtered.cn)
#Strip first row 
genie.filtered.cn.t<- as.data.frame(genie.filtered.cn.t[-1,])
# Rename Columns to be the matching genes which we know is in the same order
colnames(genie.filtered.cn.t) <- unlist(intersecting.genes)
#Make the rownames into values
genie.filtered.cn.t <- setDT(genie.filtered.cn.t,keep.rownames = TRUE)[]
# make the first column header to be SAMPLE_ID
colnames(genie.filtered.cn.t)[1] <- "SAMPLE_ID"
# Now its all READY!!!

```


Function to generate the genie subsets as well as generate the CN Profiles
```{r}
numValidFilters<-0
i<-0

makeGenieSubsetProfile <- function(filterString, cnlevel){
  
  # create entire filter command in one string
  filterString1 <- paste('filter(genie.clin,',filterString,")")  
  # run the filter command
  subsetClinical <- eval(parse(text=filterString1))
  records <- filter(genie.filtered.cn.t, SAMPLE_ID %in% subsetClinical$SAMPLE_ID)
  #print(records)
  #only subsets with more than 100 samples are valid
  #print("Grabbed Records")
  #print(nrow(records))
  if (nrow(records) < 25){
    return(NA)
  }
  else{
 # assertthat::assert_that(nrow(records) >= 100){return NULL}
  #print("We have more than 100 records")
  #numValidFilters<-numValidFilters+1
  #i<-i+1
  #print(numValidFilters)
  #print(i)
  #generate profile and return it
    return(mkProfile(records, cnlevel))
  }
}
```

Make Profiles from the generated Filter Strings
```{r}
headerLine <- c("FILTER_ID", "CN_LEVEL", unlist(intersecting.genes))
makeGenieProfileTable <- function(cnlevels,filtersDF){
  headerLine <- c("FILTER_ID", "CN_LEVEL", unlist(intersecting.genes))
  genie.subset.cn.profiles <- (data.frame(matrix(ncol = length(headerLine),nrow =0)))
  for (filter_id in filtersDF$ID){
    for (copylevel in cnlevels){
      #print(filter_id)
      subsetFilter <- filter(filtersDF,ID == filter_id)
      #print(subsetFilter[,2])
      genieProfile<-makeGenieSubsetProfile(subsetFilter[,2],copylevel)
      #print(is.na(genieProfile))
      #make row
      if(!is.na(genieProfile)){
        genie.subset.cn.profiles <- rbind(genie.subset.cn.profiles,c(filter_id,copylevel,unlist(genieProfile)[-1]))
      }
    }
      #print(i)
  }
  colnames(genie.subset.cn.profiles) <- headerLine
  genie.subset.cn.profiles
}
```

```{r}
genie.subsets1560.cn.profiles <- makeGenieProfileTable(cnlevels = cnlevels,filterIDs = c(1:1560))
genie.subset.cn.profiles <- makeGenieProfileTable(cnlevels,latestFilters2)
```

Generate DataFrame of FilterStrings and their ID
```{r}
genie.cancer.types <- setDT(genie.cancer.types,keep.rownames = TRUE)[]
colnames(genie.cancer.types)[2] <- "Count"

cancer_types <- filter(genie.cancer.types, Count > 150) %>% arrange(desc(Count))
cancer_types <- c(cancer_types[,1])

#cancer type detailed vector

top10cancers.clin <- filter(genie.clin, CANCER_TYPE %in% cancer_types)
top10detailed <- as.data.frame(summary(factor(top10cancers.clin$CANCER_TYPE_DETAILED)))
top10detailed <- setDT(top10detailed,keep.rownames = TRUE)
colnames(top10detailed)[2] <- "Count"
colnames(top10detailed)[1] <- "CANCER_TYPE_DETAILED"
detailed_cancer <- arrange(top10detailed, desc(Count))
cancer_types_detailed <- detailed_cancer$CANCER_TYPE_DETAILED
cancer_types_detailed <- cancer_types_detailed[1:15]

#Sex vector
sexes<- c("Male","Female")

#races vector
races <- c("White", "Black", "Asian")

#copy levels vector
cnlevels <- c(-2,-1,1,2)

ages <- list(list(0,18),list(19,30),list(31,40),list(19,40))
ages19_30<-list(list(19,30))
ages31_40<-list(list(31,40))
ages19_40 <-list(list(19,40))
```



Generate and Clean up results from generateFilters function
```{r}
makeFilters <- function(cancers = NA, cancer_subtypes=NA, sexes = NA, races = NA, ages = NA ){
  filterStringsTestAll <- as.data.frame(generateAllFilters(cancers,cancer_subtypes,sexes,races,ages))
  filterStringsTestAll <- setDT(filterStringsTestAll,keep.rownames = TRUE)[]
  colnames(filterStringsTestAll)[1] <- "ID"
  colnames(filterStringsTestAll)[2] <- "FilterString"
  filterStringsTestAll$ID <- as.integer(filterStringsTestAll$ID)
  filterStringsTestAll$FilterString <- as.character(filterStringsTestAll$FilterString)
  return(filterStringsTestAll)
}

```


```{r}
latestFilters <- makeFilters(cancer_types,cancerPairedWithSubtypes,sexes,races,ages)
latestFilters2 <- makeFilters(cancer_types,cancerPairedWithSubtypes,sexes,races,ages)
```

Make Profiles from the generated Filter Strings
```{r}
genieProfiles <-data.frame()
for (filter in filterStrings$FilterString){
  genieProfile<-makeGenieSubsetProfile(filter,2)
  #make row
  newRow <- append(genieRow,filterStrings$ID,after==0)
  newRow <-as.data.frame(genieProfile)
  newRow <- t(newRow)
  newRow<-as.data.frame(newRow)
  genieProfiles <- bind_rows(genieProfiles,newRow)
  
  #print(i)
}
  genieRow <- makeGenieSubsetProfile(filterStrings[4,2],2) 
  newRow <- append(genieRow,4,after=0)
  newRow <- append(newRow,2,after=1)
  newRow <- as.data.frame(newRow)
  newRow <- t(newRow)
  newRow<-as.data.frame(newRow)
  genieProfiles <- bind_rows(genieProfiles,newRow)

```



```{r}

singleFilterSet <- function(cancer=NA, cancer_subtype=NA, sex=NA, race=NA, age= NA) {
  result = ""
  if (!is.na(cancer)) result <- paste(result, "CANCER_TYPE == '", cancer, "'", sep = "")
  if (!is.na(cancer_subtype)) result <- paste(result, ", CANCER_TYPE_DETAILED == '", cancer_subtype, "'", sep = "")
  if (!is.na(sex)) result <- paste(result, ", SEX == '", sex, "'", sep = "")  
  if (!is.na(race)) result <- paste(result, ", PRIMARY_RACE == '", race, "'", sep = "")
  if (!is.na(age)) result <- paste(result, ", AGE_AT_SEQ_REPORT >= ", age[1], ", AGE_AT_SEQ_REPORT < ", age[2], sep = "")
  #if (!is.na(age)) result <- paste(result, ", AGE_AT_SEQ_REPORT < ", age[2], sep = "")
  result
}

```

Make map of cancer - subtypes of that cancer
```{r}

#t <- filter(genie.clin, genie.clin$CANCER_TYPE == "Breast Cancer")
#breastCancerSubtypes <- summary(factor(t$CANCER_TYPE_DETAILED))
cancerPairedWithSubtypes <- new.env()
for (cancer in cancer_types){
  t <- filter(genie.clin,genie.clin$CANCER_TYPE == cancer)
  #print(cancer)
  name <- paste(cancer,"Subtypes")
  name <- gsub(" ","",name)
  subtypes <- summary(factor(t$CANCER_TYPE_DETAILED))
  #print(class(name))
  #print(cancer)
  
  cancerPairedWithSubtypes[[cancer]] <- subtypes[subtypes >25]

}
```


```{r}
#testing iterating through hash map

for (cancer in cancer_types){
  print(cancer)
 
  #print(rownames(as.matrix(cancerPairedWithSubtypes[[cancer]])))
  for (i in  1:length(cancerPairedWithSubtypes[[cancer]])){
    cancer_subtype <- rownames(as.matrix(cancerPairedWithSubtypes[[cancer]]))[i]
    print(cancer_subtype)
  }
  
}
```









--------------------Keep This function at the end of the pipeline------It's long---------

```{r}

filterStrings <- data.frame(ID= c(1:15000),
                 FilterString = c(""))
generateAllFilters <- function(cancers=NA, cancer_subtypes=NA, sexes=NA, races=NA, ages= NA){
  if (is.na(cancer)){
    print("ERROR: Must input a vector of cancer types")
    return(NA)
  }
  results <- c()
  #results <- append(results, generateTier1Filters(cancers))
  results <- append(results, generateTier2Filters(cancers, cancer_subtypes))

  results <- append(results, generateTier3Filters(cancers, cancer_subtypes,sexes,races,ages))
 
  results <- append(results, generateTier4Filters(cancers, cancer_subtypes,sexes,races,ages))
  
  results <- append(results, generateTier5Filters(cancers, cancer_subtypes,sexes,races,ages))
  print(length(results))
  return(results)
}
```
  
  
  
  --------------------------------Tier 1---Least Specific, only sort by major cancer type----------------
```{r}  
generateTier1Filters <- function(cancers){  
  results<-as.character(sapply(cancers,singleFilterSet))
  return(results)
}
```


  --------------------------------Tier 2---Sort with 2 filters--------------------------------------------
```{r}
generateTier2Filters <- function(cancers=NA, cancer_subtypes=NA,sexes=NA,races=NA,ages=NA){
  results <- c()
  if (!is.na(cancer_subtypes)){
    for (cancer in cancers){
      for (i in  1:length(cancer_subtypes[[cancer]])){
        cancer_subtype <- rownames(as.matrix(cancer_subtypes[[cancer]]))[i]
        results <- append(results,singleFilterSet(cancer,cancer_subtype = cancer_subtype))
      }
    }
  }
  if (!is.na(sexes)){
    for (cancer in cancers){
      for (sex in sexes){
        results <- append(results,singleFilterSet(cancer,sex=sex))
      }
    }
  }  
  
  if (!is.na(races)){
    for (cancer in cancers){
      for (race in races){
        results <- append(results,singleFilterSet(cancer,race = race))
      }
    }
  }
  if (!is.na(ages)){
    for (cancer in cancers){
      for (age in ages){
        results <- append(results,singleFilterSet(cancer,age = age))
      }
    }
  }
  return(results)
}
```
  
  
  ----------------------------------Tier 3---Sort with 3 filters----------------------------------------
```{r}
generateTier3Filters <- function(cancers, cancer_subtypes,sexes,races,ages){
  results <- c()
  if (!is.na(cancer_subtypes) & (!is.na(sexes))){
    for (cancer in cancers){
      for (i in  1:length(cancer_subtypes[[cancer]])){
        cancer_subtype <- rownames(as.matrix(cancer_subtypes[[cancer]]))[i]
        for (sex in sexes){
          results <- append(results,singleFilterSet(cancer,cancer_subtype = cancer_subtype,sex = sex))
        }
      }
    }
  }
  if (!is.na(cancer_subtypes) & (!is.na(races))){
    for (cancer in cancers){
      for (i in  1:length(cancer_subtypes[[cancer]])){
        cancer_subtype <- rownames(as.matrix(cancer_subtypes[[cancer]]))[i]
        for (race in races){
          results <- append(results,singleFilterSet(cancer,cancer_subtype = cancer_subtype,race = race))
        }
      }
    }
  }
  if (!is.na(cancer_subtypes) & (!is.na(ages))){
    for (cancer in cancers){
      for (i in  1:length(cancer_subtypes[[cancer]])){
        cancer_subtype <- rownames(as.matrix(cancer_subtypes[[cancer]]))[i]
        for (age in ages){
          results <- append(results,singleFilterSet(cancer,cancer_subtype = cancer_subtype,age = age))
        }
      }
    }
  }
  if (!is.na(sexes) & (!is.na(races))){
    for (cancer in cancers){
      for (sex in sexes){
        for (race in races){
          results <- append(results,singleFilterSet(cancer,sex=sex,race = race))
        }
      }
    }
  }
  if (!is.na(sexes) & (!is.na(ages))){
    for (cancer in cancers){
      for (sex in sexes){
        for (age in ages){
          results <- append(results,singleFilterSet(cancer,sex = sex,age = age))
        }
      }
    }
  }
  if (!is.na(races) & (!is.na(ages))){
    for (cancer in cancers){
      for (race in races){
        for (age in ages){
          results <- append(results,singleFilterSet(cancer,race = race,age = age))
        }
      }
    }
  } 
  return(results) 
}
```
  
  
  -----------------------------------Tier 4---Sort with 4 filters-----------------------------------------
```{r}  
generateTier4Filters <- function(cancers, cancer_subtypes,sexes,races,ages){
  results <- c()
  if (!is.na(cancer_subtypes) & (!is.na(sexes)) & (!is.na(races))){
    for (cancer in cancers){
      for (i in  1:length(cancer_subtypes[[cancer]])){
        cancer_subtype <- rownames(as.matrix(cancer_subtypes[[cancer]]))[i]
        for (sex in sexes){
          for (race in races){
            results <- append(results,singleFilterSet(cancer,cancer_subtype = cancer_subtype,sex = sex, race = race))
          }
        }
      }
    }
  }
  if (!is.na(cancer_subtypes) & (!is.na(sexes)) & (!is.na(ages))){
    for (cancer in cancers){
      for (i in  1:length(cancer_subtypes[[cancer]])){
        cancer_subtype <- rownames(as.matrix(cancer_subtypes[[cancer]]))[i]
        for (sex in sexes){
          for (age in ages){
            results <- append(results,singleFilterSet(cancer,cancer_subtype = cancer_subtype,sex = sex, age = age))
          }
        }
      }
    }
  }
  if (!is.na(cancer_subtypes) & (!is.na(races)) & (!is.na(ages))){
    for (cancer in cancers){
      for (i in  1:length(cancer_subtypes[[cancer]])){
        cancer_subtype <- rownames(as.matrix(cancer_subtypes[[cancer]]))[i]
        for (race in races){
          for (age in ages){
            results <- append(results,singleFilterSet(cancer,cancer_subtype = cancer_subtype,race = race, age = age))
          }
        }
      }
    }
  }
  if (!is.na(races) & (!is.na(sexes)) & (!is.na(ages))){
    for (cancer in cancers){
      for (race in races){
        for (sex in sexes){
          for (age in ages){
            results <- append(results,singleFilterSet(cancer,sex = sex,race = race, age = age))
          }
        }
      }
    }
  }
  return(results) 
}
```

  -------------------------------------------Tier 5---Sort with all 5 filters----------------------------------
```{r}
generateTier5Filters <- function(cancers, cancer_subtypes,sexes,races,ages){
  results <- c()
  if (!is.na(cancer_subtypes) & (!is.na(sexes)) & (!is.na(races)) & (!is.na(ages))){
    for (cancer in cancers){
      for (i in  1:length(cancer_subtypes[[cancer]])){
        cancer_subtype <- rownames(as.matrix(cancer_subtypes[[cancer]]))[i]
        for (sex in sexes){
          for (race in races){
            for (age in ages){
            results <- append(results,singleFilterSet(cancer,cancer_subtype = cancer_subtype,sex = sex, race = race,age = age))
            }
          }
        }
      }
    }
  }
  return(results)
}
```